Estimating Planetary Habitability via Particle Swarm Optimization of CES Production Functions.

### 2018-01-17 docs/report/draft.tex
Finished running time tests.

The plots in Figures~\ref{fig:distcdcrs} and~\ref{fig:distcddrs} indicate the distribution of the CDHS across the
exoplanets tested from the PHL-EC.\@ Figures~\ref{fig:itercdcrs} and~\ref{fig:itercddrs} show the distribution of
iterations required to converge to a global maxima. The spike at 0 is caused by particles converging to a $\gbest$ that
does not shift from the original position (for a more detailed explanation see Appendix \ref{app:con}). The plots in
Figures~\ref{fig:distcedrs} and~\ref{fig:distcedrs} indicate the distribution of the CEESA score across the exoplanets,
while Figures~\ref{fig:itercedrs} and~\ref{fig:itercecrs} indicate the distribution of iterations to convergence. These
graphs aggregate the results of optimizing the Habitability Production Functions (Equations~\ref{eq:cdhscrs},
~\ref{eq:cdhsdrs},~\ref{eq:ceesadrs} and~\ref{eq:ceesacrs}) for each exoplanet in the PHL-EC by the method described in
Algorithm~\ref{alg:cop}.

>>>>

The plots in Figures~\ref{fig:distcdcrs} and~\ref{fig:distcddrs} describe the distribution of the CDHS across exoplanets
tested from the PHL-EC.\@ Figures~\ref{fig:itercdcrs} and~\ref{fig:itercddrs} show the distribution of iterations
required to converge to a global maxima. The spike at 0 is caused by particles converging to a $\gbest$ that does not
shift from the original position (for a more detailed explanation see Appendix~\ref{app:con}). The plots in
Figures~\ref{fig:distcedrs} and~\ref{fig:distcedrs} describe the distribution of the CEESA score across the exoplanets,
while Figures~\ref{fig:itercedrs} and~\ref{fig:itercecrs} show the distribution of iterations to convergence. These
graphs aggregate the results of optimizing the Habitability Production Functions
(Equations~\ref{eq:cdhscrs},~\ref{eq:cdhsdrs},~\ref{eq:ceesadrs} and~\ref{eq:ceesacrs}) for each exoplanet in the PHL-EC
by the method described in Algorithm~\ref{alg:cop}.
